Notes on Perturbational Quantities

### 2008-09-19 docs/pert_notes/paper.tex
texism
starting on updates to the doc

{\bf What the code did before 8/6/08:} 

@@

There is no {\tt correct\_base} function for $(\rho h)_0$ written yet, nor is any adjustment made 
to sync up $(\rho h)_0$ after the thermal diffusion step.\\ \\
{\bf What the code currently does:}  Define $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  
and $(\rho h)' = (\rho h)^{(1)}-(\rho h)_0^{(1)}$.  Then we predict $(\rho h)'$ to 

@@

(\ref{rhohprime equation}) as the forcing. \MarginPar{{\tt full\_rhoh0\_evolution} comes into play here}

@@

\begin{table*}
\begin{center}
\caption{Quantity that is created in mkflux and passed into update scal\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\subsubsection{Advancing $(\rho h)_0$}
{\bf Using full\_rhoh0\_evolution = F:}  Define 
$(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  
and $(\rho h)' = (\rho h)^{(1)}-(\rho h)_0^{(1)}$.  Then, $(\rho h)_0^{(1)} \rightarrow$ 
{\tt advect\_base} $\rightarrow (\rho h)_0^{(2)}$.\\ \\
{\bf Using full\_rhoh0\_evolution = T:}

@@

There is no {\tt correct\_base} function for $(\rho h)_0$ written yet, nor is any 
adjustment made to sync up $(\rho h)_0$ after the thermal diffusion step.
We predict $(\rho h)'$ to 

@@

(\ref{rhohprime equation}) as the forcing, except that we omit the $\psi$ in the forcing for plane-parallel, and we omit the $\partial w_0/\partial r$ part of $\psi$ in spherical.  Note that we still use full $\psi$ to update the cell.

@@

\begin{table*}
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}
